### 2017-01-10 eg6-letters/analysis-note-vf/experimental_setup.tex
update the NIM paper

\subsection{Inner calorimeter}
In the basic setup of CLAS, the photons are detected by the forward 
electromagnetic calorimeters (EC) which cover polar angles from 8$^{\circ}$ to 
45$^{\circ}$. With a 6 GeV electron beam, a large part of the DVCS photons are 
produced at polar angles below 15$^{\circ}$, where the acceptance of the EC
is small. In the CLAS-E1DVCS experiment (2005), CLAS was upgraded with the 
addition of an Inner Calorimeter (IC). This calorimeter covers completely the 
polar angles between 5$^{\circ}$ and 15$^{\circ}$. Figure \ref{fig:CLAS_RTPC_2} 
shows a schematic plot of our experimental setup. The front face of the IC is 
facing the downstream side of the Radial TPC (RTPC) and placed at 16 cm from 
the center of CLAS.\\

@@

\subsection{Solenoid}
At occupancies greater than 4$\%$, the efficiency of the drift chambers 
starts to drop and the resolution gets worse. The first region of the DCs (R1) 
has a higher occupancy than the other two regions (R2 and R3), mostly due to 
noise. This noise mainly comes from the M\o ller electrons, which are 
low-energy electrons produced in the scattering of the electron beam on the 
target's electrons. To reduce the effect of the noise, CLAS was upgraded by 
adding a solenoid that surrounds the target. The magnet provides a nominal 
field of 4.5 T at the center of the target. This solenoid deflects the produced 
M\o ller electrons to very forward angles preventing them from arriving to the 
drift chamber, the IC or the RTPC. Figure \ref{fig:solenoid} shows a GEANT3 simulation of the 
M\o ller electrons tracks without applying the solenoid field (left), and how 
these electrons are bent to low polar angles, less than 4$^{\circ}$, when the 
solenoid field is applied.\\

>>>>

\subsection{Inner calorimeter}
In the basic setup of CLAS, the photons are detected by the forward 
electromagnetic calorimeters (EC) which cover polar angles from 8$^{\circ}$ to 
45$^{\circ}$. With a 6 GeV electron beam, a large part of the DVCS photons are 
produced at polar angles below 15$^{\circ}$, where the acceptance of the EC
is small. In the CLAS-E1DVCS experiment (2005), CLAS was upgraded with the 
addition of an Inner Calorimeter (IC). This calorimeter covers completely the 
polar angles between 5$^{\circ}$ and 15$^{\circ}$. Figure \ref{fig:CLAS_RTPC_2} 
shows a schematic plot of our experimental setup. The front face of the IC is 
facing the downstream side of the Radial TPC (RTPC) and placed at 16 cm from 
the center of CLAS.

@@

\subsection{Solenoid}
At occupancies greater than 4$\%$, the efficiency of the drift chambers 
starts to drop and the resolution gets worse. The first region of the DCs (R1) 
has a higher occupancy than the other two regions (R2 and R3), mostly due to 
noise. This noise mainly comes from the M\o ller electrons, which are 
low-energy electrons produced in the scattering of the electron beam on the 
target's electrons. To reduce the effect of the noise, CLAS was upgraded by 
adding a solenoid that surrounds the target. The magnet provides a nominal 
field of 4.5 T at the center of the target. This solenoid deflects the produced 
M\o ller electrons to very forward angles preventing them from arriving to the 
drift chamber, the IC or the RTPC. Figure \ref{fig:solenoid} shows a GEANT3 simulation of the 
M\o ller electrons tracks without applying the solenoid field (left), and how 
these electrons are bent to low polar angles, less than 4$^{\circ}$, when the 
solenoid field is applied.

### 2017-01-10 eg6-letters/analysis-note-vf/ref.tex
update the NIM paper

>>>>

\bibitem{Vadim_priv}
   Private communications with V.~Guzey based on reference 
   \cite{{EMC_vadim_3}}.

\bibitem{Guidal_priv}
   Private communications with M.~Guidal based on reference:   M.~Guidal, 
   M.~V.~Polyakov, A.~V.~Radyushkin and M.~Vanderhaeghen, Nucleon form-factors 
   from generalized parton distributions,
     Phys.\ Rev.\ D {\bf 72}, 054013, [hep-ph/0410251], 2005.

\bibitem{GonzalezHernandez:2012jv} Private communications with S.~Liuti based 
   on:  J.~O.~Gonzalez-Hernandez, S.~Liuti, G.~R.~Goldstein and K.~Kathuria,
     Interpretation of the Flavor Dependence of Nucleon Form Factors in a 
     Generalized Parton Distribution Model, Phys.\ Rev.\ C {\bf 88}, no. 6, 
     065206, arXiv:1206.1876 [hep-ph], 2013.

### 2017-01-10 eg6-letters/eg6-letters/NIM/EG6_RTPC_NIM.tex
update the NIM paper

\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
\usepackage{graphicx}  
\usepackage{dcolumn}   
\usepackage{bm}        
\usepackage{amssymb}

% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
processes, $^4$He nucleus remains intact and recoils as a whole in the final 
state. The CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for 
similar studies on proton targets, however it cannot track recoils with momenta 
less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
using CLAS spectrometer, which was upgraded with the RTPC. The detector was 
positioned directly around the gaseous target, allowing a detection threshold 
of $~$125  MeV/c for $^4$He. This article discuses the RTPC design, work 
principle, developed calibration methods and detector performance.
\end{abstract}

@@

\section{\label{sec:level1} Introduction}

@@

This paper is organized in this way: section \ref{prev_tpc} presents an 
overview of the TPCs history and previous usage, section \ref{sec_design} 
details the physics considerations for the RTPC design and its internal 
structure, while section \ref{sec_readout} points the properties of the 
read-out system.  The calibration strategies for such detectors will be 
discussed in section \ref{sec_calib}. Finally, the performance of the RTPC is 
discussed in section \ref{sec_perf}.

\section{TPCs overview}
In the late 1970s, David R. Nygren presented the concept of the Time projection 
Chambers (TPCs) as a new tool to track charged particles based on combining 
electric and magnetic fields within a sensitive gas volume. The ionized 
electrons are collected by a position-sensitive electron collection system.  
Later in 1997, F.~Sauli introduced the Gas Electron Multiplier (GEM) as an 
effective gas-gain element to improve the tracking efficiency of the TPCs 
\ref{gem_sauli}.

The first implementation of a RTPC in CLAS have been achieved for the BoNuS 
experiment~\cite{BONUS} in 200x. The success of this detector for the detection 
of slow protons motivated the development of this new RTPC. For the channel of 
interests of our experiments, the recoiled $^{4}He$ nuclei have momentum per 
charge around 150 MeV/c, the detection of these particles was the primary 
motivation for using such design.

\section{CLAS-EG6 RTPC design} \label{sec_design}
The RTPC is a 200~mm long with a 150~mm diameter time projection chamber. The 
ionized electrons are drifting outward perpendicularly to the beam direction.  
These electrons are then amplified by three layers of GEMs and detected on 4.45 
by 5~mm pads. As for BoNuS, the RTPC has two detection parts but unlike BoNuS 
they are part of a single chamber. Each part has independent GEM amplification 
systems that cover around 80\% of the azimuthal angle. Under the effect of the 
electromagnetic field, the ionization electrons drift to the readout system on 
the external shell with a curved trajectory as can be seen in the 
figure~\ref{fig:RTPC_1_4}.

\begin{figure}[tb]
\centering
\includegraphics[scale=0.19]{fig/RTPC_exp.png}
\caption[]{\small\sf View of the RTPC ready to be inserted in the solenoid. } 
\label{fig:RTPC2}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.28]{fig/RTPC_1_all.png}
\caption[]{\small\sf Schematic drawing of the RTPC taken on a plane 
perpendicular to the beam line, see text for description of the elements.} 
\label{fig:RTPC_1_4}
\end{figure}

As seen in figure~\ref{fig:RTPC2}, the RTPC is composed from the beam axis to 
the exterior by:\\
\begin{itemize}
   \item The target, filled with 5~atm $^4$He, has a 3~mm radius with Kapton 
      walls only 27$\mu$m thick.

@@

   \item The GEM system is composed of three GEMs located at radii, 60 mm, 63 
      mm and 66 mm, they amplify the electrons to make a measurable signal.

   \item The readout board has internal radius of 69~mm and collects the 
      charges, preamplifiers are plugged directly on its outer side and are 
      transmitting the signal to the data acquisition electronics.
\end{itemize}
\begin{figure}[tb]
\centering
\includegraphics[scale=0.70]{fig/GEM_photo.jpg}
\caption[]{A schematic layout of the GEMs system in one module of the RTPC.} 
\label{fig:GEMs}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.4]{fig/RunNumber_61551_TDCmax_Zslice.png}
\caption[]{\small\sf Time profile distribution for the collected hits in one experimental run. } 
\label{fig:RunNumber_61551_TDCmax_Zslice}
\end{figure}

@@

\begin{figure}[tb]
\hspace*{-1.8cm}
\includegraphics[scale=0.28]{fig/Drift_run_number_1.png}
\caption[]{\small\sf $TDC_{Nbmax/2}$ versus the experimental run numbers (time). } 
\label{fig:Drift_run_number_1}
\end{figure}

@@

The drift path is the trajectory which an electron follows in the gas. The standard software to calculate drift paths is the MAGBOLTZ program ~\cite{MAGBOLTZ}. For its calculations, MAGBOLTZ needs to know the detector's geometry, the exact composition of the gas mixture and of course the electric and the magnetic fields. We used such calculations as a first calibration, but as can be seen with the drift speed, conditions are far from stable in the chamber. Moreover, because we use of a thin foil as a cathode, the geometry knowledge is limited to a millimeter precision. These problems, already encountered for the BoNuS RTPC calibration (ref), have motivated the acquisition of specific calibration runs. These are taken with lower energy electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic process ($e ^{4}He \rightarrow e ^{4}He$). In this process the knowledge of the electron kinematic gives us the helium nuclei kinematic and therefore allow us to calibrate our drift paths independently of our knowledge of the exact conditions in the chamber.

@@

\begin{figure}[tb]
\centering
%\hspace{-0.95cm}
\includegraphics[scale=0.37]{fig/R_correlation.png}
\caption[]{\small\sf R versus TDC distribution for the simulated hits locating in a single $z$ bin. The maximum $R$ equals 60 mm (close to the anode) at minimum TDCs (Trigger time is 15), and minimum R equals 30 mm (close to the cathode) at maximum TDCs ($\sim75$).}
\label{fig:R_correlation}
\end{figure}

\begin{itemize}
\item The linear assumption between R and time(TDC) is necessary to link the generated hits from GEANT4 to physical hits. Figure \ref{fig:R_correlation} shows our initial $R$ versus TDC. \\
\item For these selected hits, we look at $\Delta\phi$ ($\Delta \phi$ = $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC. We clearly obtain a correlation shown in figure~\ref{fig:1st_pass_delta_phi}. This $\Delta \phi$ change with TDC shows the drift in $phi$ of the electrons due to the Lorentz angle. \\

\begin{figure}[tb]
\centering
\includegraphics[scale=0.37]{fig/1st_pass_delta_phi.png}
\caption[]{\small\sf $\Delta \phi$ versus TDC distribution for the simulated hits locating in one slice centered at 35 mm.}
\label{fig:1st_pass_delta_phi}
\end{figure}

\item Using this first measurement, we can calculate a new correlation between $R$ and TDC. The result, shown in figure~\ref{fig:R_TDC}, is very close to linear explaining the fast convergence of our procedure. \\

\begin{figure}[tb]
\centering
\includegraphics[scale=0.37]{fig/R_TDC.png}
\caption[]{\small\sf The calculated R versus the time is corrected by the parameters of $\Delta \phi$ from the first pass.}
\label{fig:R_TDC}
\end{figure}

\item In the second pass, we associate simulated helium positions to physical hits according to their calculated correlation and obtain new $\Delta \phi$ distributions.\\
\item We finally parametrize the $\Delta\phi$ distributions with a fit as can be seen in figure~\ref{fig:DELTA_PHI_TDC}, which shows the final $\Delta \phi$ versus TDC with a red line representing our drift paths fit.
\end{itemize}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.37]{fig/DELTA_PHI_TDC.png}
\caption[]{\small\sf $\Delta \phi$ versus TDC distribution in the second pass for the slice centered at 35 mm longitudinal position along the RTPC. The red line represents the final drift paths in this slice.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

@@

\begin{figure}[tb]
\includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
\caption[]{\small\sf Simulated (upper) and experimental (lower) ADCs and TDCs distributions of a track. The colors indicate the pads, same color in top and bottom indicate that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

\begin{figure}[tb]
\includegraphics[scale=0.26]{fig/dedx_p_exp_1st.png}
\caption[]{\small\sf $\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ is calculated using the gains of the first method. The lines are theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H (d).}
\label{fig:dedx_p_exp_1st}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.26]{fig/dedx_p_exp_2nd.png}
\caption[]{\small\sf $\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ is calculated using the gains of the second method. The lines are theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H (d).}
\label{fig:dedx_p_exp_2nd}
\end{figure}

@@

\begin{figure}[tb]
\hspace{-0.4cm}
\includegraphics[scale=0.27]{fig/noisy_pad_before_rejection.png}
\caption[]{\small\sf }
\label{fig:noisy_pad_before_rejection}
\end{figure}

\begin{figure}[tb]
\hspace{-0.4cm}
\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection.png}
\caption[]{\small\sf }
\label{fig:noisy_pad_after_rejection}
\end{figure}

>>>>

\documentclass[twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}  
\usepackage{amssymb}  
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue, citecolor=blue}

@@

\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
processes, $^4$He nucleus remains intact and recoils as a whole in the final 
state. The CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for 
similar studies on proton targets, however it cannot track recoils with momenta 
less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
using CLAS spectrometer, which was upgraded with the RTPC during the CLAS-EG6 
experimental run. The detector was positioned directly around the gaseous 
target, allowing a detection threshold of $~$100  MeV/c for $^4$He. This 
article discuses the RTPC design, work principle, developed calibration methods 
and detector performance.
\end{abstract}

@@

\section{Introduction} \label{sec:level1}

@@

In this paper we report the progress in designing and calibrating a radial TPC 
that had been used with JLab-CLAS spectrometer. This paper is organized in this 
way: section \ref{prev_tpc} presents an overview of the TPCs history and 
previous usage, section \ref{sec_design} details the physics considerations for 
the RTPC design and its internal structure, while section \ref{sec_readout} 
points the properties of the read-out system.  The calibration strategies for 
such a detector is discussed in section \ref{sec_calib}. Finally, the 
performance of the RTPC is described
in section \ref{sec_perf}.

\section{TPC technology} \label{prev_tpc}
In the late 1970s, David R. Nygren presented the concept of the Time projection 
Chambers (TPCs) as a new tool to track charged particles based on combining 
electric and magnetic fields within a sensitive gas volume. The ionized 
electrons are collected by a position-sensitive electron collection system.  
Later in 1997, F.~Sauli introduced the Gas Electron Multiplier (GEM) as an 
effective gas-gain element to improve the tracking efficiency of the TPCs 
\ref{gem_sauli}. Currently, the TPCs are widely used in physics experiments, 
such as high-energy physics (ALEPH, DELPHI), heavy-ion physics (STAR, ALICE) 
and rare-event searches (XENON, NEXT).

The first implementation of a radial TPC with JLab-CLAS spectrometer has been 
performed by the BoNuS experiment \cite{BONUS} in 2005. The success of the 
BoNuS-RTPC in detecting the slow protons motivated the development of this new 
RTPC. For the channel of interests of our experiments, the recoiled $^{4}He$ 
nuclei have momentum per charge around 150 MeV/c, the detection of these 
particles was the primary motivation for designing this detector.

\section{CLAS-EG6 RTPC design} \label{sec_design}
The design of CLAS-EG6 RTPC has been chosen according to physics and 
experimental considerations. At 6 GeV incident electron beam energy, the recoil 
$^{4}He$ nuclei, from the coherent DVCS channel, have an average momentum (per 
charge) around 125 MeV/c, while the "standard" CLAS detects charged particles 
with a threshold of 250 MeV/c. On the experimental site, The chosen design has 
to fit within the available space of a 5 Tesla Solenoid magnet that surrounds 
the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows an experimental view 
of the RTPC before inserting it into the solenoid.

The CLAS-EG6 RTPC is a 200~mm long with a 150~mm diameter time projection 
chamber. While a charged particle traverses a gas-sensitive volume, the ionized 
electrons are released and drift outward perpendicularly to the beam direction.  
These electrons are then amplified by three layers of GEMs and detected on 4.45 
by 5~mm pads. As for CLAS-BoNuS, the EG6-RTPC has two detection parts but 
unlike BoNuS they are part of a single chamber. Each part has independent GEM 
amplification systems that cover around 80\% of the azimuthal angle. Under the 
effect of the electromagnetic field, the ionization electrons drift to the 
readout system on the external shell with a curved trajectory as can be seen in 
the figure~\ref{fig:RTPC_1_4}.

\begin{figure}[tb]
\centering
\includegraphics[scale=0.19]{fig/RTPC_exp.png}
\caption{View of the RTPC ready to be inserted in the solenoid. } 
\label{fig:RTPC2}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.28]{fig/RTPC_1_all.png}
\caption{Schematic drawing of the RTPC taken on a plane perpendicular to the 
beam line, see text for description of the elements.} \label{fig:RTPC_1_4}
\end{figure}

As seen in figure~\ref{fig:RTPC_1_4}, the RTPC has the following substructure, 
from the beam axis to the exterior::\\
\begin{itemize}
   \item The target extends along the RTPC's central z-axis, with a diameter of 
      6 mm. It is enclosed in a 27-$\mu$m-thick Kapton wall.

@@

   \item The GEM system is composed of three GEMs located at radii, 60 mm, 63 
      mm and 66 mm, they amplify the electrons to make a measurable signal. In 
      this configuration, the first GEM layer represents the anode.

   \item The readout board has internal radius of 69~mm and collects the 
      charges, preamplifiers are plugged directly on its outer side and are 
      transmitting the signal to the data acquisition electronics.
\end{itemize}

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.70]{fig/GEM_photo.jpg}
\caption{A schematic layout of the GEMs system in one module of the RTPC.} 
\label{fig:GEMs}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[scale=0.4]{fig/RunNumber_61551_TDCmax_Zslice.png}
\caption{Time profile distribution for the collected hits in one experimental 
run. } \label{fig:RunNumber_61551_TDCmax_Zslice}
\end{figure}

@@

\begin{figure}[tb]
\hspace*{-1.8cm}
\includegraphics[scale=0.28]{fig/Drift_run_number_1.png}
\caption{$TDC_{Nbmax/2}$ versus the experimental run numbers (time).  } 
\label{fig:Drift_run_number_1}
\end{figure}

@@

The drift paths are the trajectories which an electron follows in the gas. The 
standard software to calculate drift paths is the MAGBOLTZ program 
~\cite{MAGBOLTZ}. For its calculations, MAGBOLTZ needs to know the detector's 
geometry, the exact composition of the gas mixture and of course the electric 
and the magnetic fields. We used such calculations as a first calibration, but 
as can be seen with the drift speed, conditions are far from stable in the 
chamber. Moreover, because we use of a thin foil as a cathode, the geometry 
knowledge is limited to a millimeter precision. These problems, already 
encountered for the BoNuS RTPC calibration (ref), have motivated the 
acquisition of specific calibration runs. These are taken with lower energy 
electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
process ($e ^{4}He \rightarrow e ^{4}He$). In this process the knowledge of the 
electron kinematic gives us the helium nuclei kinematic and therefore allow us 
to calibrate our drift paths independently of our knowledge of the exact 
conditions in the chamber.

@@

\begin{figure}[tb]
\centering
%\hspace{-0.95cm}
\includegraphics[scale=0.37]{fig/TdcR_check_p1_10.png}
\caption{R versus TDC distribution for the simulated hits locating in a single 
$z$ bin. The maximum $R$ equals 60 mm (close to the anode) at minimum TDCs 
(Trigger time is 15), and minimum R equals 30 mm (close to the cathode) at 
maximum TDCs ($\sim75$).}
\label{fig:R_correlation}
\end{figure}

\begin{itemize}

   \item The linear assumption between R and time(TDC) is necessary to link the 
      generated hits from GEANT4 to physical hits. Figure 
      \ref{fig:R_correlation} shows our initial $R$ versus TDC.

   \item For these selected hits, we look at $\Delta\phi$ ($\Delta \phi$ = 
      $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC. We clearly obtain a 
      correlation shown in figure~\ref{fig:1st_pass_delta_phi}. This $\Delta 
      \phi$ change with TDC shows the drift in $phi$ of the electrons due to 
      the Lorentz angle.

      \begin{figure}[tb]
         \centering
         \includegraphics[scale=0.37]{fig/TdcPhi_p1_10.png}
         \caption{$\Delta \phi$ versus TDC distribution for the simulated hits 
         locating in one slice centered at 35 mm.}
         \label{fig:1st_pass_delta_phi}
      \end{figure}

   \item Using this first measurement, we can calculate a new correlation 
      between $R$ and TDC. The result, shown in figure~\ref{fig:R_TDC}, is very 
      close to linear explaining the fast convergence of our procedure.

      \begin{figure}[tb]
         \centering
         \includegraphics[scale=0.37]{fig/R_TDC.png}
         \caption{The calculated R versus the time is corrected by the 
         parameters of $\Delta \phi$ from the first pass.}
         \label{fig:R_TDC}
      \end{figure}

   \item In the second pass, we associate simulated helium positions to 
      physical hits according to their calculated correlation and obtain new 
      $\Delta \phi$ distributions.

   \item We finally parametrize the $\Delta\phi$ distributions with a fit as 
      can be seen in figure~\ref{fig:DELTA_PHI_TDC}, which shows the final 
      $\Delta \phi$ versus TDC with a red line representing our drift paths 
      fit.
\end{itemize}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.37]{fig/FitResult_p2_10.png}
\caption{$\Delta \phi$ versus TDC distribution in the second pass for the slice 
centered at 35 mm longitudinal position along the RTPC. The red line represents 
the final drift paths in this slice.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

@@

\begin{figure}[tb]
\includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
\caption{Simulated (upper) and experimental (lower) ADCs and TDCs distributions 
of a track. The colors indicate the pads, same color in top and bottom indicate 
that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

\begin{figure}[tb]
   \includegraphics[scale=0.26]{fig/dedx_p_exp_1st.png}
   \caption{$\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the 
      RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ 
   is calculated using the gains of the first method.  The lines are 
theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and 
$^2$H (d).}
\label{fig:dedx_p_exp_1st}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.26]{fig/dedx_p_exp_2nd.png}
\caption{$\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the 
   RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ is 
   calculated using the gains of the second method.  The lines are theoretical 
   expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H 
(d).}
\label{fig:dedx_p_exp_2nd}
\end{figure}

@@

\begin{figure}[tb]
\hspace{-0.4cm}
\includegraphics[scale=0.27]{fig/noisy_pad_before_rejection.png}
\caption{}
\label{fig:noisy_pad_before_rejection}
\end{figure}

\begin{figure}[tb]
\hspace{-0.4cm}
\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection.png}
\caption{}
\label{fig:noisy_pad_after_rejection}
\end{figure}

### 2017-01-10 eg6-letters/final_checks/DVCS-CAN-Meeting-Comments.tex
update the NIM paper

 \item Regarding the request of cutting the tails and comparing the 
reconstructed coherent asymmetries to the ones without cutting the tails, the 
asymmetries are presented in fig \ref{fig:BSA_ME_bins_sig} as a function of 
$\phi$ in bins in $Q^{2}$, $x_{B}$ and $-t$. The $Q^{2}$, $x_{B}$ and $-t$ 
dependences of $A_{LU}$ at $\phi = 90 ^{\circ}$, from fitting the signals in 
fig \ref{fig:BSA_ME_bins_sig}, are presented in fig \ref{ig:ALU_ME_bins_sig} 
with and without cutting the tails in the missing energy distribution.  One can 
conclude that the two sets are compatible within the given error bars.

>>>>

 \item Regarding the request of cutting the tails and comparing the 
reconstructed coherent asymmetries to the ones without cutting the tails, the 
asymmetries are presented in fig \ref{fig:BSA_ME_bins_sig} as a function of 
$\phi$ in bins in $Q^{2}$, $x_{B}$ and $-t$. The $Q^{2}$, $x_{B}$ and $-t$ 
dependences of $A_{LU}$ at $\phi = 90 ^{\circ}$, from fitting the signals in 
fig \ref{fig:BSA_ME_bins_sig}, are presented in fig \ref{fig:ALU_ME_bins_sig} 
with and without cutting the tails in the missing energy distribution. One can 
conclude that the two sets are compatible within the given error bars.
